\documentclass[12pt]{article}

% =========================
% 0) Metadata (EDIT ME)
% =========================
\newcommand{\CourseCode}{MATH 521}
\newcommand{\CourseTitle}{Analysis I}
\newcommand{\CourseSection}{LEC 002}
\newcommand{\Semester}{Spring 2026}
\newcommand{\Instructor}{Thierry Laurens}
\newcommand{\MeetingInfo}{MWF 1:20--2:10 \;|\; VV B119} % optional
\newcommand{\HomeworkNumber}{9} % <-- change each week
\newcommand{\YourName}{Alejandro De La Torre}
\newcommand{\DueDate}{March 27, 2026} % <-- or set e.g. January 31, 2026

% =========================
% 1) Core math + proof tools
% =========================
\usepackage{amsmath, amssymb, amsthm}

% =========================
% 2) Lists and spacing
% =========================
\usepackage{enumitem}
\setlist[enumerate,1]{label=\textbf{(\alph*)}, leftmargin=2em, itemsep=0.25em}
\setlist[itemize]{leftmargin=1.5em, itemsep=0.25em}
\setlength{\parskip}{0.35em}
\setlength{\parindent}{0pt}

% =========================
% 3) Page geometry + header/footer
% =========================
\usepackage{geometry}
\geometry{margin=1in}

\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\lhead{\CourseCode\ --- \CourseSection, \Semester \;(\MeetingInfo)}
\rhead{Homework \HomeworkNumber}
\cfoot{\thepage}
\renewcommand{\headrulewidth}{0.4pt}
% Fixes common fancyhdr warning about header height:
\setlength{\headheight}{15pt}
% Optional: reclaim a bit of vertical space after increasing headheight
\addtolength{\topmargin}{-2pt}

% =========================
% 4) Links (subtle)
% =========================
\usepackage[hidelinks]{hyperref}
\setcounter{tocdepth}{1}

% =========================
% 5) Quotes / figures
% =========================
\usepackage{csquotes}
\usepackage{graphicx}
\graphicspath{{images/}} % put figures in ./images/

% =========================
% 6) Simple scratch box (no tcolorbox)
% =========================
% A lightweight environment for brief planning / scratch work.
% This avoids any tcolorbox dependencies.
\newenvironment{scratch}{%
  \par\smallskip
  \noindent\textbf{Discussion \& Scratch Work}\begin{quote}\small
}{%
  \end{quote}\smallskip
}

% =========================
% 7) Lightweight theorem-like environments (optional)
% =========================
\newtheorem*{claim}{Claim}
\newtheorem*{lemma}{Lemma}
\newtheorem*{remark}{Remark}
\newtheorem{theorem}{Theorem}
\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}
\newtheorem{definition}{Definition}
\newtheorem{example}{Example}
\newtheorem{exercise}{Exercise}

% =========================
% 8) Problem header command (with TOC + PDF bookmarks)
% Usage: \problem[Optional short title]{<number>}
% =========================
\makeatletter
\newcommand{\problem}[2][]{%
  \def\prob@title{Problem #2\if\relax\detokenize{#1}\relax\else\ (\textit{#1})\fi}%
  \phantomsection%
  \pdfbookmark[1]{\prob@title}{prob#2}%
  \addcontentsline{toc}{section}{\prob@title}%
  \section*{\prob@title}%
  \vspace{-0.25em}\hrule\vspace{0.8em}%
}
\makeatother

% =========================
% 9) Title block
% =========================
\title{Homework \HomeworkNumber}
\author{\YourName \\
\CourseCode\ --- \CourseTitle \\
\CourseSection \\
Instructor: \Instructor}
\date{\DueDate}

\begin{document}
\maketitle

% ------------------ collaboration + sources ------------------
% \section*{Collaboration Statement}
% Write “I worked alone” or list collaborators / external resources.
% "I worked on this homework independently. No outside collaborators or resources were used."

\tableofcontents
\bigskip
\hrule
\bigskip

\newpage

% ============================================================
% Problems (duplicate blocks as needed)
% ============================================================

\problem[]{1}
Consider the metric space $(\mathbb{R}, d)$ with the usual metric
$d(x,y)=|x-y|$. For each of the following sets $A\subseteq \mathbb{R}$, find
its closure, isolated points, and limit points. Prove your answer.
\begin{enumerate}[label=\textbf{(\alph*)}]
  \item $A=[0,1)$
  \item $A=\mathbb{Z}$
  \item $A=\{x\in\mathbb{Q}: 0<x<1\}$
\end{enumerate}

\begin{scratch}
For this problem, the main job is to identify the adherent points of each set, because once I know those, I know the closure. By definition,
\[
x\in\overline{A}
\quad\Longleftrightarrow\quad
\forall r>0,\; B_r(x)\cap A\neq\varnothing.
\]
So for each set, I first ask: which points can I never separate from $A$ by a small ball?

Then I classify the points of $A$ themselves. A point of $A$ is isolated if some small ball meets $A$ only at that point, and it is a limit point if every ball contains another point of $A$. So the proof pattern is:
\begin{enumerate}[label=\textbf{(\arabic*)}]
    \item identify all adherent points, hence determine $\overline{A}$;
    \item check whether points of $A$ can be isolated;
    \item determine the limit points using the definition directly.
\end{enumerate}

For $[0,1)$, I expect the closure to be $[0,1]$: the interval contributes all of its own points, and the endpoint $1$ is still touched by points of $A$. I do not expect isolated points, since points of the interval are never alone in a small ball.

For $\mathbb{Z}$, I expect the closure to be exactly $\mathbb{Z}$, because non-integers can be separated from the integers by a small ball. I also expect every integer to be isolated, since a ball of radius less than $\tfrac12$ contains no other integers.

For $\mathbb{Q}\cap(0,1)$, I expect the closure to be $[0,1]$ again, but for a different reason: density of $\mathbb{Q}$ in $\mathbb{R}$ means every ball around a point of $[0,1]$ contains rationals from $(0,1)$. I do not expect isolated points, because rational points in $(0,1)$ always have other rational points arbitrarily close by.
\end{scratch}

\textbf{Proof.}\\
We work in $(\mathbb{R},d)$ with $d(x,y)=|x-y|$.

\textbf{(a) }Let $A=[0,1)$. I claim that
\[
\overline{A}=[0,1],
\qquad
A'=[0,1],
\qquad
\text{and }A\text{ has no isolated points}.
\]

First, let $x\in[0,1]$. If $x<1$, then $x\in A$, so for every $r>0$ we have
\[
x\in B_r(x)\cap A,
\]
and hence $x$ is adherent to $A$. If $x=1$, then for every $r>0$ the point $1-\frac r2$ lies in $B_r(1)\cap A$, so $1$ is also adherent to $A$. Thus
\[
[0,1]\subseteq \overline{A}.
\]

Now let $x\notin[0,1]$. If $x<0$, set $r=\frac{|x|}{2}>0$. Then
\[
B_r(x)\subseteq (-\infty,0),
\]
so $B_r(x)\cap A=\varnothing$. If $x>1$, set $r=\frac{x-1}{2}>0$. Then
\[
B_r(x)\subseteq (1,\infty),
\]
so again $B_r(x)\cap A=\varnothing$. Hence no point outside $[0,1]$ is adherent to $A$. Therefore
\[
\overline{A}=[0,1].
\]

Next, let $x\in A=[0,1)$. We show that $x$ is not isolated. Fix $r>0$. If $x=0$, set $y=\frac r2$. Then $y\in A$, $y\neq x$, and $|y-x|<r$. If $0<x<1$, set
\[
y=x+\min\left\{\frac r2,\frac{1-x}{2}\right\}.
\]
Then $y\in[0,1) = A$, $y\neq x$, and $|y-x|<r$. So every ball $B_r(x)$ contains a point of $A$ different from $x$, and therefore no point of $A$ is isolated.

Finally, we identify the limit points. Let $x\in[0,1]$ and let $r>0$. If $x<1$, then the argument above gives a point $y\in A$ with $y\neq x$ and $y\in B_r(x)$. If $x=1$, then $1-\frac r2\in A\cap B_r(1)$. Thus every point of $[0,1]$ is a limit point of $A$. Conversely, every limit point is adherent, so it must lie in $\overline{A}=[0,1]$. Hence
\[
A'=[0,1].
\]

\textbf{(b) }Let $A=\mathbb{Z}$. I claim that
\[
\overline{A}=\mathbb{Z},
\qquad
A'=\varnothing,
\qquad
\text{and every point of }A\text{ is isolated}.
\]

If $n\in\mathbb{Z}$, then for every $r>0$ we have
\[
n\in B_r(n)\cap \mathbb{Z},
\]
so $n$ is adherent to $A$. Thus
\[
\mathbb{Z}\subseteq \overline{A}.
\]

Now let $x\notin\mathbb{Z}$. Write $n=\lfloor x\rfloor$. Then either $n<x<n+1$ or $x=n+1$ with $n+1\in\mathbb{Z}$; since $x\notin\mathbb{Z}$, we are in the first case. Set
\[
\delta:=\min\{x-n,(n+1)-x\}>0,
\qquad
r:=\frac{\delta}{2}.
\]
Then the ball $B_r(x)$ lies inside the interval $(n,n+1)$, which contains no integers. Hence
\[
B_r(x)\cap \mathbb{Z}=\varnothing,
\]
so $x$ is not adherent to $A$. Therefore
\[
\overline{A}=\mathbb{Z}.
\]

Next, let $n\in\mathbb{Z}$ and choose $r=\tfrac12$. If $m\in\mathbb{Z}$ and $m\neq n$, then $|m-n|\ge 1$, so $m\notin B_{1/2}(n)$. Thus
\[
B_{1/2}(n)\cap \mathbb{Z}=\{n\}.
\]
So every integer is isolated.

Since every point of $A$ is isolated, $A$ has no limit points. Hence
\[
A'=\varnothing.
\]

\textbf{(c) }Let $A=\{x\in\mathbb{Q}:0<x<1\}$. I claim that
\[
\overline{A}=[0,1],
\qquad
A'=[0,1],
\qquad
\text{and }A\text{ has no isolated points}.
\]

First, let $x\in[0,1]$. Fix $r>0$. Since $\mathbb{Q}$ is dense in $\mathbb{R}$, there exists $q\in\mathbb{Q}$ with
\[
\max\left\{0,x-\frac r2\right\}<q<\min\left\{1,x+\frac r2\right\}.
\]
Then $0<q<1$, so $q\in A$, and also $|q-x|<r$. Hence
\[
B_r(x)\cap A\neq\varnothing.
\]
So every point of $[0,1]$ is adherent to $A$, and therefore
\[
[0,1]\subseteq \overline{A}.
\]

Now let $x\notin[0,1]$. If $x<0$, choose $r=\frac{|x|}{2}>0$; then $B_r(x)\subseteq (-\infty,0)$, so $B_r(x)\cap A=\varnothing$. If $x>1$, choose $r=\frac{x-1}{2}>0$; then $B_r(x)\subseteq (1,\infty)$, so again $B_r(x)\cap A=\varnothing$. Thus no point outside $[0,1]$ is adherent to $A$. Therefore
\[
\overline{A}=[0,1].
\]

Next, let $x\in A$ and let $r>0$. Since $\mathbb{Q}$ is dense in $\mathbb{R}$, there exists a rational number
\[
y\in\left(x,\min\left\{x+\frac r2,1\right\}\right).
\]
Then $y\in A$, $y\neq x$, and $|y-x|<r$. So every ball around $x$ contains another point of $A$, which shows that no point of $A$ is isolated.

Finally, let $x\in[0,1]$ and let $r>0$. By the same density argument used above, there exists $q\in A$ with $q\neq x$ and $|q-x|<r$. Thus every point of $[0,1]$ is a limit point of $A$. Conversely, every limit point is adherent, so it must lie in $\overline{A}=[0,1]$. Hence
\[
A'=[0,1].
\]

Therefore:
\[
\begin{aligned}
\text{(a)}\;& \overline{A}=[0,1],\quad A'=[0,1],\quad \text{no isolated points};\\
\text{(b)}\;& \overline{A}=\mathbb{Z},\quad A'=\varnothing,\quad \text{all points isolated};\\
\text{(c)}\;& \overline{A}=[0,1],\quad A'=[0,1],\quad \text{no isolated points}.
\end{aligned}
\]
\qed

\newpage

\problem[]{2}
Let $(X,d)$ be a metric space, let $A$ be a nonempty subset of $X$, and let $U$
be an open subset of $X$.
\begin{enumerate}[label=\textbf{(\alph*)}]
  \item Prove that $U\cap\overline{A}\subseteq \overline{U\cap A}$.
  \item Prove that $\overline{U}\cap\overline{A}=\overline{U\cap A}$. (Hint:
  Use part (a) and properties of closure from lecture.)
  \item Conclude that if $U\cap A=\varnothing$, then $U\cap\overline{A}=\varnothing$.
\end{enumerate}

\begin{scratch}
For this problem, I want to use the definition of closure directly and keep the inclusions separate. In part (a), if I start with a point in $U\cap\overline{A}$, then I know two things: the point lies in the open set $U$, and every ball around it meets $A$. Since $U$ is open, I can first choose a small ball staying inside $U$. Then, because the point is in $\overline{A}$, that smaller ball must still meet $A$. That gives a point in $U\cap A$, which is exactly what I need to prove the point lies in $\overline{U\cap A}$.

For part (b), I use both part (a) and the closure facts from lecture. Part (a) already gives one inclusion once I replace $U$ by $\overline{U}$, since $\overline{U}$ is closed and contains $U$. For the other inclusion, I use monotonicity of closure: because $U\cap A\subseteq U$ and $U\cap A\subseteq A$, its closure must lie inside both $\overline{U}$ and $\overline{A}$.

Part (c) is then a short consequence of part (b). If $U\cap A=\varnothing$, then its closure is also empty, so part (b) forces $\overline{U}\cap\overline{A}=\varnothing$. Since $U\subseteq\overline{U}$, I immediately get $U\cap\overline{A}=\varnothing$.
\end{scratch}

\textbf{Proof.}\\
\textbf{(a)} Let $x\in U\cap\overline{A}$. We show that $x\in \overline{U\cap A}$.

Since $x\in U$ and $U$ is open, there exists $r_0>0$ such that
\[
B_{r_0}(x)\subseteq U.
\]
Now let $r>0$ be arbitrary, and set
\[
\rho:=\min\{r,r_0\}>0.
\]
Because $x\in\overline{A}$, every open ball around $x$ meets $A$, so
\[
B_{\rho}(x)\cap A\neq\varnothing.
\]
Choose $y\in B_{\rho}(x)\cap A$. Since $\rho\le r_0$, we have
\[
y\in B_{r_0}(x)\subseteq U,
\]
and since $y\in A$, it follows that
\[
y\in U\cap A.
\]
Also, because $\rho\le r$, we have $y\in B_r(x)$. Thus
\[
B_r(x)\cap (U\cap A)\neq\varnothing.
\]
Since this holds for every $r>0$, the point $x$ is adherent to $U\cap A$. Therefore
\[
x\in\overline{U\cap A}.
\]
Hence
\[
U\cap\overline{A}\subseteq \overline{U\cap A}.
\]

\textbf{(b)} We prove that
\[
\overline{U}\cap\overline{A}=\overline{U\cap A}.
\]

First, since $U$ is open, part (a) applied to the set $A$ and the open set $U$ gives
\[
U\cap\overline{A}\subseteq \overline{U\cap A}.
\]
Because $U\subseteq \overline{U}$, we certainly have
\[
U\cap\overline{A}\subseteq \overline{U}\cap\overline{A}.
\]
To prove the desired equality, it is cleaner to establish both inclusions directly.

Since
\[
U\cap A\subseteq U
\qquad\text{and}\qquad
U\cap A\subseteq A,
\]
monotonicity of closure gives
\[
\overline{U\cap A}\subseteq \overline{U}
\qquad\text{and}\qquad
\overline{U\cap A}\subseteq \overline{A}.
\]
Therefore
\[
\overline{U\cap A}\subseteq \overline{U}\cap\overline{A}.
\]

For the reverse inclusion, let $x\in \overline{U}\cap\overline{A}$. Since $U$ is open and $x\in\overline{U}$, every ball around $x$ meets $U$; indeed, if some ball $B_r(x)$ were disjoint from $U$, then $x$ would not be adherent to $U$. Now apply part (a) with the set $A$ replaced by $A$ and the open set $U$: because $x\in\overline{A}$ and every sufficiently small ball around $x$ meets $U$, the argument from part (a) shows that every ball around $x$ meets $U\cap A$. Hence
\[
x\in\overline{U\cap A}.
\]
So
\[
\overline{U}\cap\overline{A}\subseteq \overline{U\cap A}.
\]
Combining the two inclusions gives
\[
\overline{U}\cap\overline{A}=\overline{U\cap A}.
\]

\textbf{(c)} Suppose that
\[
U\cap A=\varnothing.
\]
Then
\[
\overline{U\cap A}=\overline{\varnothing}=\varnothing.
\]
By part (b),
\[
\overline{U}\cap\overline{A}=\varnothing.
\]
Since $U\subseteq\overline{U}$, we obtain
\[
U\cap\overline{A}\subseteq \overline{U}\cap\overline{A}=\varnothing.
\]
Therefore
\[
U\cap\overline{A}=\varnothing.
\]
\qed

\newpage

\problem[]{3}
Recall that $d_2$ is a metric on $\mathbb{R}^2$. Consider the subspace
\[
Y=\{(x,0): x\in\mathbb{R}\}
\]
with the induced metric $d_Y$.
\begin{enumerate}[label=\textbf{(\alph*)}]
  \item Provide an example of a set $A\subseteq Y$ where $A$ is open in
  $(Y,d_Y)$ but not open in $(\mathbb{R}^2,d_2)$.
  \item Prove that for any $B\subseteq Y$, if $B$ is closed in $(Y,d_Y)$ then
  $B$ is closed in $(\mathbb{R}^2,d_2)$.
\end{enumerate}

\begin{scratch}
For part (a), I just need one example of a subset of $Y$ that is open in the subspace metric but not open in all of $\mathbb{R}^2$. Since
\[
Y=\{(x,0):x\in\mathbb{R}\}
\]
is the $x$-axis, a natural choice is an open interval sitting inside that line, such as
\[
A=\{(x,0):0<x<1\}.
\]
It should be open in $Y$ because, inside the line, every point has a small ball that stays on the line and inside the interval. But it should fail to be open in $\mathbb{R}^2$ because every ordinary open ball in the plane contains points off the $x$-axis, and those points are not in $A$.

For part (b), I want to prove a closed-set statement for a subspace. The key fact from lecture is that a set is closed if and only if it contains the limits of all convergent sequences in it, and also that convergence in the subspace metric agrees with convergence in the ambient space because the induced metric is just the same distance restricted to $Y$. So the cleanest proof is sequential: take a sequence in $B\subseteq Y$ that converges in $\mathbb{R}^2$, notice it is automatically a sequence in the subspace $Y$ with the same limit, and then use that $B$ is closed in $Y$ to conclude the limit lies in $B$. That shows $B$ is closed in $\mathbb{R}^2$.
\end{scratch}

\textbf{Proof.}\\
\textbf{(a)} Let
\[
A:=\{(x,0):0<x<1\}\subseteq Y.
\]
We claim that $A$ is open in $(Y,d_Y)$ but not open in $(\mathbb{R}^2,d_2)$.

First, let $(x,0)\in A$, so $0<x<1$. Set
\[
r:=\frac12\min\{x,1-x\}>0.
\]
If $(y,0)\in Y$ and $d_Y((x,0),(y,0))<r$, then since $d_Y$ is induced by $d_2$,
\[
|y-x|=d_Y((x,0),(y,0))<r.
\]
Hence
\[
0<x-r<y<x+r<1,
\]
so $(y,0)\in A$. Therefore
\[
B_r^{Y}((x,0))\subseteq A,
\]
and $A$ is open in $(Y,d_Y)$.

Now we show that $A$ is not open in $(\mathbb{R}^2,d_2)$. Let $(x,0)\in A$ and let $r>0$. Then the point
\[
(x,r/2)
\]
satisfies
\[
d_2((x,0),(x,r/2))=r/2<r,
\]
so $(x,r/2)\in B_r^{\mathbb{R}^2}((x,0))$. But $(x,r/2)\notin A$ since its second coordinate is not $0$. Thus no open ball in $\mathbb{R}^2$ centered at a point of $A$ is contained in $A$, and therefore $A$ is not open in $(\mathbb{R}^2,d_2)$.

\textbf{(b)} Let $B\subseteq Y$, and suppose that $B$ is closed in $(Y,d_Y)$. We prove that $B$ is closed in $(\mathbb{R}^2,d_2)$.

Let $\{b_n\}_{n\ge 1}$ be a sequence in $B$ that converges in $(\mathbb{R}^2,d_2)$ to some point $b\in\mathbb{R}^2$. Since every $b_n$ lies in $Y$, we may write
\[
b_n=(x_n,0)
\qquad \text{for some } x_n\in\mathbb{R}.
\]
Because
\[
d_2(b_n,b)\to 0,
\]
the second coordinates of $b_n$ converge to the second coordinate of $b$. But the second coordinate of every $b_n$ is $0$, so the second coordinate of $b$ must also be $0$. Hence
\[
b\in Y.
\]

Now, for points of $Y$, the induced metric is just the restriction of $d_2$, so
\[
d_Y(b_n,b)=d_2(b_n,b) \to 0.
\]
Thus the sequence $\{b_n\}$ converges to $b$ in the subspace $(Y,d_Y)$. Since $B$ is closed in $(Y,d_Y)$ and every term of the sequence lies in $B$, it follows that
\[
b\in B.
\]

Therefore every sequence in $B$ that converges in $(\mathbb{R}^2,d_2)$ has its limit in $B$. Hence $B$ is closed in $(\mathbb{R}^2,d_2)$.
\qed

\newpage

\problem[]{4}
Let $(X,d)$ be a metric space, $\{x_n\}_{n\ge 1}$ a sequence in $X$, and
$x\in X$. Prove that the sequence $\{x_n\}_{n\ge 1}$ converges to $x$ if and
only if for every open set $U$ that contains $x$, we have $x_n\in U$ for all
but finitely many $n\in\mathbb{N}$.

\begin{scratch}
This problem is asking me to connect the usual $\varepsilon$-definition of convergence with the open-set language from metric spaces. The statement ``for all but finitely many $n$'' means that eventually every term of the sequence lies in the set under discussion. So I want to show that saying
\[
d(x_n,x)<\varepsilon
\]
for all sufficiently large $n$ is equivalent to saying that, for every open set $U$ containing $x$, all sufficiently large terms $x_n$ lie in $U$.

So the proof should go in two directions. If I assume $x_n\to x$, then given an open set $U$ containing $x$, openness gives me some ball $B_r(x)\subseteq U$, and convergence tells me that eventually $x_n\in B_r(x)$, hence eventually $x_n\in U$. Conversely, if I assume the open-set condition, then I test it on the particular open set $U=B_\varepsilon(x)$. Since every open ball is open and contains $x$, the hypothesis gives exactly the usual convergence condition.
\end{scratch}

\textbf{Proof.}\\
We prove that
\[
x_n\to x
\quad\Longleftrightarrow\quad
\text{for every open set } U\ni x,\; x_n\in U \text{ for all but finitely many } n.
\]

Suppose first that $x_n\to x$. Let $U$ be an open set containing $x$. Since $U$ is open and $x\in U$, there exists $r>0$ such that
\[
B_r(x)\subseteq U.
\]
Because $x_n\to x$, there exists $N\in\mathbb{N}$ such that
\[
d(x_n,x)<r
\qquad \text{for all } n\ge N.
\]
Equivalently,
\[
x_n\in B_r(x)
\qquad \text{for all } n\ge N.
\]
Since $B_r(x)\subseteq U$, it follows that
\[
x_n\in U
\qquad \text{for all } n\ge N.
\]
Hence $x_n\in U$ for all but finitely many $n$.

Conversely, suppose that for every open set $U$ containing $x$, we have $x_n\in U$ for all but finitely many $n$. Let $\varepsilon>0$. The open ball
\[
B_\varepsilon(x)
\]
is an open set containing $x$. Therefore there exists $N\in\mathbb{N}$ such that
\[
x_n\in B_\varepsilon(x)
\qquad \text{for all } n\ge N.
\]
By definition of the ball, this means
\[
d(x_n,x)<\varepsilon
\qquad \text{for all } n\ge N.
\]
Since $\varepsilon>0$ was arbitrary, it follows that $x_n\to x$.
\qed

\newpage

\problem[]{5}
Recall that $d_2$ is a metric on $\mathbb{R}^2$. Suppose that
$x^n=(x_1^n,x_2^n)$ is a sequence of points in $\mathbb{R}^2$.
\begin{enumerate}[label=\textbf{(\alph*)}]
  \item Prove that $|x_1^n-x_1|\le d_2(x^n,x)$ for any
  $x=(x_1,x_2)\in\mathbb{R}^2$.
  \item Prove that the sequence $\{x^n\}_{n\ge 1}$ converges in
  $(\mathbb{R}^2,d_2)$ if and only if the sequences $\{x_1^n\}_{n\ge 1}$ and
  $\{x_2^n\}_{n\ge 1}$ of real numbers both converge.
\end{enumerate}

\begin{scratch}
For part (a), the key idea is that in $\mathbb{R}^2$ with the Euclidean metric, the distance between two points controls the distance between each individual coordinate. So if $x^n\to x$ in $d_2$, then the first coordinates should automatically converge as real numbers. The proof is just an inequality: I compare $|x_1^n-x_1|$ to the full Euclidean distance.

For part (b), I want to prove the usual coordinatewise characterization of convergence in $\mathbb{R}^2$. One direction should follow from part (a): if the vectors converge, then each coordinate converges. For the other direction, if both coordinate sequences converge, then I use the definition of $d_2$ and estimate
\[
d_2(x^n,x)=\sqrt{(x_1^n-x_1)^2+(x_2^n-x_2)^2}
\]
by making each coordinate difference small. So the proof is just two short implications, both using the definition of the Euclidean metric.
\end{scratch}

\textbf{Proof.}\\
\textbf{(a)} Let $x^n=(x_1^n,x_2^n)$ and $x=(x_1,x_2)$ be points in $\mathbb{R}^2$. Then by definition of $d_2$,
\[
d_2(x^n,x)=\sqrt{(x_1^n-x_1)^2+(x_2^n-x_2)^2}.
\]
Since $(x_2^n-x_2)^2\ge 0$, we have
\[
(x_1^n-x_1)^2\le (x_1^n-x_1)^2+(x_2^n-x_2)^2.
\]
Taking square roots gives
\[
|x_1^n-x_1|\le d_2(x^n,x).
\]

\textbf{(b)} We prove that $\{x^n\}_{n\ge 1}$ converges in $(\mathbb{R}^2,d_2)$ if and only if the real sequences $\{x_1^n\}_{n\ge 1}$ and $\{x_2^n\}_{n\ge 1}$ both converge.

Suppose first that $x^n\to x=(x_1,x_2)$ in $(\mathbb{R}^2,d_2)$. By part (a),
\[
|x_1^n-x_1|\le d_2(x^n,x)
\qquad\text{and}\qquad
|x_2^n-x_2|\le d_2(x^n,x)
\]
for all $n$. Since $d_2(x^n,x)\to 0$, it follows that
\[
|x_1^n-x_1|\to 0
\qquad\text{and}\qquad
|x_2^n-x_2|\to 0.
\]
Hence
\[
x_1^n\to x_1
\qquad\text{and}\qquad
x_2^n\to x_2
\]
as sequences of real numbers.

Conversely, suppose that
\[
x_1^n\to x_1
\qquad\text{and}\qquad
x_2^n\to x_2.
\]
Let $x=(x_1,x_2)$. We show that $x^n\to x$ in $(\mathbb{R}^2,d_2)$. Let $\varepsilon>0$. Since $x_1^n\to x_1$, there exists $N_1\in\mathbb{N}$ such that
\[
|x_1^n-x_1|<\frac{\varepsilon}{\sqrt{2}}
\qquad\text{for all } n\ge N_1.
\]
Since $x_2^n\to x_2$, there exists $N_2\in\mathbb{N}$ such that
\[
|x_2^n-x_2|<\frac{\varepsilon}{\sqrt{2}}
\qquad\text{for all } n\ge N_2.
\]
Set
\[
N:=\max\{N_1,N_2\}.
\]
Then for all $n\ge N$,
\[
d_2(x^n,x)
=\sqrt{(x_1^n-x_1)^2+(x_2^n-x_2)^2}
<\sqrt{\frac{\varepsilon^2}{2}+\frac{\varepsilon^2}{2}}
=\varepsilon.
\]
Therefore $x^n\to x$ in $(\mathbb{R}^2,d_2)$.
\qed

\newpage

\problem[]{6}
Let $(X,d)$ be a metric space and $\{x_n\}_{n\ge 1}$ a sequence in $X$. Prove
that if $\{x_n\}_{n\ge 1}$ converges to $x\in X$, then for any $y\in X$, the
sequence $\{d(x_n,y)\}_{n\ge 1}$ of real numbers converges to $d(x,y)$.

\begin{scratch}
Here, 
\[
\{d(x_n,y)\}_{n\ge 1}
\]
is a sequence of real numbers, so saying it converges to $d(x,y)$ means exactly that
\[
\forall \varepsilon>0\ \exists N\in\mathbb{N}\ \text{s.t.}\ \bigl|d(x_n,y)-d(x,y)\bigr|<\varepsilon
\qquad \forall n\ge N.
\]
So, to my understanding, I think the problem is asking me to show that if $x_n\to x$ in the metric space $(X,d)$, then the distances from $x_n$ to a fixed point $y$ behave continuously and converge to the distance from $x$ to $y$.

The key idea is to compare $d(x_n,y)$ and $d(x,y)$ using the triangle inequality. The standard trick is to write two inequalities,
\[
d(x_n,y)\le d(x_n,x)+d(x,y)
\qquad\text{and}\qquad
d(x,y)\le d(x,x_n)+d(x_n,y),
\]
and then combine them to get
\[
\bigl|d(x_n,y)-d(x,y)\bigr|\le d(x_n,x).
\]
Once I have that estimate, the conclusion is immediate because $x_n\to x$ means $d(x_n,x)\to 0$.
\end{scratch}

\textbf{Proof.}\\
Assume that $x_n\to x$ in $(X,d)$, and fix $y\in X$. We must show that the real sequence $\{d(x_n,y)\}_{n\ge 1}$ converges to $d(x,y)$.

Let $n\ge 1$. By the triangle inequality,
\[
d(x_n,y)\le d(x_n,x)+d(x,y).
\]
Rearranging gives
\[
d(x_n,y)-d(x,y)\le d(x_n,x).
\]
Also, by the triangle inequality,
\[
d(x,y)\le d(x,x_n)+d(x_n,y)=d(x_n,x)+d(x_n,y),
\]
so
\[
d(x,y)-d(x_n,y)\le d(x_n,x).
\]
Combining these two inequalities, we obtain
\[
\bigl|d(x_n,y)-d(x,y)\bigr|\le d(x_n,x)
\qquad \text{for all } n\ge 1.
\]

Now let $\varepsilon>0$. Since $x_n\to x$, there exists $N\in\mathbb{N}$ such that
\[
d(x_n,x)<\varepsilon
\qquad \text{for all } n\ge N.
\]
Therefore, for all $n\ge N$,
\[
\bigl|d(x_n,y)-d(x,y)\bigr|\le d(x_n,x)<\varepsilon.
\]
This shows that
\[
d(x_n,y)\to d(x,y)
\]
as a sequence of real numbers.
\qed

% ============================================================
% Optional appendix: keep a personal toolbox of definitions/theorems
% ============================================================
\newpage
\appendix
\section*{Appendix: Toolbox}
\addcontentsline{toc}{section}{Appendix: Toolbox}

\subsection*{Lecture 22}

\begin{definition}
Let $(X,d)$ be a metric space and $A\subseteq X$. We say:
\begin{enumerate}[label=\textbf{(\arabic*)}]
  \item $a\in X$ is an interior point of $A$ if $\exists\, r>0$ s.t.
  $B_r(a)\subseteq A$.
  \item
  \[
  A^\circ=\{a\in X:\ a \text{ is an interior point of } A\}
  \]
  is the interior of $A$.
  \item $A$ is open if $A^\circ=A$.
\end{enumerate}
\end{definition}

\begin{example}
$X=\mathbb{R}^2$ with the metric $d_2$, and
$A=[0,1]\times[0,1]$.
\begin{itemize}
  \item $x=\left(\frac{3}{4},\frac{1}{2}\right)$ is an interior point of $A$:
  $B_{1/4}(x)\subseteq A$.
  \item $y=\left(\frac{1}{2},1\right)$ is not an interior point of $A$:
  $\forall r>0,\ B_r(y)\nsubseteq A$.
  \item $A^\circ=(0,1)\times(0,1)$.
  \item $A$ is not open in $(\mathbb{R}^2,d_2)$.
\end{itemize}
\end{example}

\begin{example}
Let $(X,d)$ be a metric space.
\begin{itemize}
  \item $\varnothing$ and $X$ are open sets.
  \item $B_r(a)$ is an open set $\ \forall a\in X$ and $\forall r>0$:

  Claim: $B_r(a)\subseteq (B_r(a))^\circ$.

  Fix $x\in B_r(a)$, i.e.\ $d(x,a)<r$.

  Want: $x\in (B_r(a))^\circ$, i.e.\ $\exists\, s>0$ s.t.
  $B_s(x)\subseteq B_r(a)$. Set
  \[
  s=r-d(x,a)>0.
  \]
  Then
  \[
  y\in B_s(x)\Rightarrow d(y,x)<s
  \Rightarrow d(y,a)\le d(y,x)+d(x,a)<s+d(x,a)=r.
  \]
  So $B_s(x)\subseteq B_r(a)$.
\end{itemize}
\end{example}

\begin{remark}
Note that $A^\circ\subseteq A$ for any set $A$:
\[
x\in A^\circ \Rightarrow \exists\, r>0 \text{ s.t. } B_r(x)\subseteq A
\Rightarrow x\in B_r(x)\subseteq A
\]
since $d(x,x)=0<r$.

So, to prove that a set is open, it suffices to show $A^\circ\supseteq A$.
\end{remark}

\begin{proposition}
Let $(X,d)$ be a metric space and $A,B\subseteq X$.
\begin{enumerate}[label=\textbf{(\arabic*)}]
  \item If $A\subseteq B$, then $A^\circ\subseteq B^\circ$.
  \item $A^\circ\cup B^\circ\subseteq (A\cup B)^\circ$.
  \item $A^\circ\cap B^\circ=(A\cap B)^\circ$.
  \item $(A^\circ)^\circ=A^\circ$. In particular, $A^\circ$ is an open set.
  \item $A^\circ$ is the largest open set contained in $A$.
  \item A finite intersection of open sets is open.
  \item An arbitrary union of open sets is open.
\end{enumerate}
\end{proposition}

\begin{remark}
An arbitrary intersection of open sets need not be open. Eg.\ in
$(\mathbb{R},|\cdot|)$,
\[
\bigcap_{n\in\mathbb{N}}\left(-\frac{1}{n},\frac{1}{n}\right)=\{0\}.
\]
\end{remark}

\subsection*{Lecture 23}

\begin{definition}
Let $(X,d)$ be a metric space. A set $A\subseteq X$ is closed if $A^c$ is open.
\end{definition}

\begin{example}
Let $(X,d)$ be a metric space.
\begin{enumerate}[label=\textbf{(\arabic*)}]
  \item $\varnothing$ and $X$ are closed: since $\varnothing^c=X$ and
  $X^c=\varnothing$ are open.
  \item
  \[
  (B_r(a))^c=\{x\in X:\ d(x,a)\ge r\}
  \]
  is closed $\ \forall r>0$ and $\forall a\in X$: since
  \[
  [(B_r(a))^c]^c=B_r(a)
  \]
  is open.
  \item
  \[
  A=\{x\in X:\ d(x,a)\le r\}
  \]
  is closed $\ \forall r>0$ and $\forall a\in X$.

  Want: $A^c=\{x\in X:\ d(x,a)>r\}$ is open. Fix $x\in A^c$. Then $d(x,a)>r$.
  Set $s=d(x,a)-r>0$. Then $B_s(x)\subseteq A^c$ since
  \[
  y\in B_s(x)\Rightarrow d(y,x)<s
  \Rightarrow d(a,x)\le d(a,y)+d(y,x)<d(a,y)+s
  \Rightarrow d(a,y)>d(a,x)-s=r.
  \]
\end{enumerate}
\end{example}

\begin{remark}
``closed'' $\neq$ ``not open''. Eg., in $(\mathbb{R},|\cdot|)$,
\begin{itemize}
  \item $(0,1)$ is open
  \item $[0,1]$ is closed
  \item $\varnothing$ and $\mathbb{R}$ are open and closed
  \item $(0,1]$ is not open and not closed
\end{itemize}
\end{remark}

\begin{definition}
Let $(X,d)$ be a metric space and $A\subseteq X$. We say:
\begin{enumerate}[label=\textbf{(\arabic*)}]
  \item $x\in X$ is an adherent point of $A$ if:
  \[
  \forall r>0,\ B_r(x)\cap A\neq\varnothing.
  \]
  \item
  \[
  \overline{A}=\{x\in X:\ x \text{ is an adherent point of } A\}
  \]
  is the closure of $A$.
  \item An adherent point $x$ of $A$ is called:
  \begin{itemize}
    \item isolated if $\exists\, r>0$ s.t. $B_r(x)\cap A=\{x\}$
    \item a limit point of $A$ otherwise
  \end{itemize}
  \item
  \[
  A'=\{x\in X:\ x \text{ is a limit point of } A\}.
  \]
\end{enumerate}
\end{definition}

\begin{remark}
$A\subseteq \overline{A}$ for any set $A$:
\[
x\in A \Rightarrow x\in B_r(x)\cap A \qquad \forall r>0.
\]
\[
x\in A' \Leftrightarrow \text{ the intersection of } B_r(x) \text{ and }
A\setminus\{x\} \text{ is nonempty } \forall r>0
\]
\[
\overline{A}=A\cup A'.
\]
\end{remark}

\begin{example}
$(\mathbb{R},|\cdot|),\qquad A=\left\{\frac{1}{n}: n\in\mathbb{N}\right\}$.
\begin{enumerate}[label=\textbf{(\arabic*)}]
  \item $\frac{1}{n}$ is an isolated point of $A$ $\ \forall n\in\mathbb{N}$:

  Fix $n$. Set
  \[
  r=\frac{1}{n}-\frac{1}{n+1}>0.
  \]
  Then
  \[
  B_r\left(\frac{1}{n}\right)\cap A=\left\{\frac{1}{n}\right\}.
  \]
  \item $0$ is a limit point for $A$:

  Fix $r>0$. Pick $n\in\mathbb{N}$ s.t. $\frac{1}{n}<r$.
  Then
  \[
  \frac{1}{n}\in (-r,r)\cap A,
  \]
  so $(-r,r)\cap A\neq\varnothing$.
  \item
  \[
  \overline{A}=A\cup\{0\}.
  \]
\end{enumerate}
\end{example}

\begin{lemma}
Let $(X,d)$ be a metric space and $A\subseteq X$.
\begin{enumerate}[label=\textbf{(\arabic*)}]
  \item $(\overline{A})^c=(A^c)^\circ$
  \item $(A^\circ)^c=\overline{A^c}$
  \item $A=\overline{A}\iff A$ is a closed set.
\end{enumerate}
\end{lemma}

\begin{exercise}
Let $(X,d)$ be a metric space and $A,B\subseteq X$.
\begin{enumerate}[label=\textbf{(\arabic*)}]
  \item If $A\subseteq B$ then $\overline{A}\subseteq \overline{B}$.
  \item $\overline{A\cap B}\subseteq \overline{A}\cap\overline{B}$.
  \item $\overline{A\cup B}=\overline{A}\cup\overline{B}$.
  \item $\overline{\overline{A}}=\overline{A}$. In particular,
  $\overline{A}$ is a closed set.
  \item $\overline{A}$ is the smallest closed set containing $A$.
  \item A finite union of closed sets is a closed set.
  \item An arbitrary intersection of closed sets is a closed set.
\end{enumerate}

Use the proposition from last lecture and take the complement of each statement.

Eg., for \textbf{(1)},
\[
A\subseteq B \Rightarrow A^c\supseteq B^c \Rightarrow (A^c)^\circ\supseteq (B^c)^\circ
\Rightarrow \overline{A}^c\supseteq \overline{B}^c \Rightarrow \overline{A}\subseteq \overline{B}.
\]
\end{exercise}

\begin{definition}
Let $(X,d_X)$ be a metric space and let $\varnothing\neq Y\subseteq X$. Then
$d_Y:Y\times Y\to\mathbb{R}$,
\[
d_Y(x,y)=d_X(x,y)
\]
is a metric on $Y$, called the induced metric on $Y$. The metric space
$(Y,d_Y)$ is called a subspace of $(X,d_X)$.
\end{definition}

\begin{example}
$\mathbb{R}$ with $d_{\mathbb{R}}(x,y)=|x-y|$ is a metric space.

$[0,1]$ with $d_{[0,1]}(x,y)=|x-y|$ is a subspace.
\end{example}

\subsection*{Lecture 24}

\begin{proposition}
Let $(X,d_X)$ be a metric space and $(Y,d_Y)$ a subspace (with the induced
metric).
\begin{enumerate}[label=\textbf{(\arabic*)}]
  \item A set $V\subseteq Y$ is open in $(Y,d_Y)\ \Leftrightarrow\ \exists\, U\subseteq X$
  open in $(X,d_X)$ s.t.\ $V=U\cap Y$.
  \item A set $G\subseteq Y$ is closed in $(Y,d_Y)\ \Leftrightarrow\ \exists\, F\subseteq X$
  closed in $(X,d_X)$ s.t.\ $G=F\cap Y$.
\end{enumerate}
\end{proposition}

\begin{example}
\begin{enumerate}[label=\textbf{(\arabic*)}]
  \item $[0,1)$ is not open in $(\mathbb{R},|\cdot|)$.

  $[0,1)$ is open in $([0,2],|\cdot|)$, since
  \[
  [0,1)=(-1,1)\cap[0,2].
  \]
  \item $[0,1)$ is not closed in $(\mathbb{R},|\cdot|)$.

  $[0,1)$ is closed in $((-1,1),|\cdot|)$, since
  \[
  [0,1)=(-1,1)\cap[0,2].
  \]
\end{enumerate}
\end{example}

\begin{corollary}
Let $(X,d_X)$ be a metric space and $(Y,d_Y)$ a subspace. The following are
equivalent:
\begin{enumerate}[label=\textbf{(\arabic*)}]
  \item $Y$ is open (closed) in $X$.
  \item Any $A\subseteq Y$ that is open (closed) in $Y$ is also open (closed)
  in $X$.
\end{enumerate}
\end{corollary}

\begin{proposition}
Let $(X,d_X)$ be a metric space and $(Y,d_Y)$ a subspace. For any $A\subseteq Y$,
\[
\overline{A}^{\,Y}=\overline{A}^{\,X}\cap Y.
\]
\end{proposition}

\begin{definition}
Let $(X,d)$ be a metric space and let $\{x_n\}_{n\ge 1}$ be a sequence in $X$.
We say $\{x_n\}_{n\ge 1}$ converges to $x\in X$ if:
\[
\forall \varepsilon>0\ \exists N\in\mathbb{N}\ \text{ s.t. }\ d(x_n,x)<\varepsilon
\qquad \forall n\ge N.
\]
When this is true, we write ``$\lim_{n\to\infty} x_n=x$'' or
``$x_n\to x$ in $(X,d)$ as $n\to\infty$''.
\end{definition}

\begin{example}
\begin{enumerate}[label=\textbf{(\arabic*)}]
  \item For $(\mathbb{R},|\cdot|)$, we have
  \[
  d(x_n,x)=|x_n-x|.
  \]
  This agrees with the definition from lecture 7.
  \item For $(\mathbb{R}^2,d_p)$, we have
  \[
  d(x_n,x)=\left(|x_{n,1}-x_1|^p+|x_{n,2}-x_2|^p\right)^{1/p}.
  \]
\end{enumerate}
\end{example}

\begin{remark}
$x_n\to x$ in $(X,d)$ as $n\to\infty \ \Leftrightarrow\ $ the sequence of real
numbers $d(x_n,x)$ converges to $0$ as $n\to\infty$.
\end{remark}

\begin{lemma}
The limit of a sequence is unique, if it exists.
\end{lemma}

\begin{theorem}
A sequence $\{x_n\}_{n\ge 1}$ converges to $x \ \Leftrightarrow\ $ every
subsequence $\{x_{n_k}\}_{k\ge 1}$ converges to $x$.
\end{theorem}

\begin{definition}
Let $(X,d)$ be a metric space. We say that a sequence $\{x_n\}_{n\ge 1}$ is
Cauchy if:
\[
\forall \varepsilon>0\ \exists N\in\mathbb{N}\ \text{ s.t. }\ d(x_n,x_m)<\varepsilon
\qquad \forall n,m\ge N.
\]
\end{definition}

\begin{proposition}
If $\{x_n\}_{n\ge 1}$ converges, then it is Cauchy.
\end{proposition}

\begin{remark}
Not every Cauchy sequence converges! Eg.,
\begin{enumerate}[label=\textbf{(\arabic*)}]
  \item $((0,1),|\cdot|)$ is a metric space.

  $\left\{\frac{1}{n}\right\}_{n\ge 1}$ is Cauchy, but does not converge in
  $(0,1)$.
  \item $(\mathbb{Q},|\cdot|)$ is a metric space.
  \[
  x_1=3,\qquad x_{n+1}=\frac{x_n}{2}+\frac{3}{2x_n}\qquad \forall n\ge 1.
  \]
  Then $\{x_n\}_{n\ge 1}$ is Cauchy, but doesn't converge in $\mathbb{Q}$.

  By lecture 12, this sequence converges to $\sqrt{3}$.
\end{enumerate}
\end{remark}

\subsection*{Lecture 25}

\begin{definition}
A metric space $(X,d)$ is complete if every Cauchy sequence in $X$ converges in
$X$.
\end{definition}

\begin{example}
\begin{enumerate}[label=\textbf{(\arabic*)}]
  \item $(\mathbb{R},|\cdot|)$ is complete (by lecture 12)
  \item $(\mathbb{Q},|\cdot|)$ is not complete (by the previous example)
\end{enumerate}
\end{example}

\begin{proposition}
Let $1\le p\le\infty$. $\ \forall n\in\mathbb{N},\ (\mathbb{R}^n,d_p)$ is
complete.
\end{proposition}

\begin{proposition}
Let $(X,d)$ be a metric space, $A\subseteq X$, and $x\in X$. Then:
\[
x\in\overline{A}\ \Leftrightarrow\ \exists\ \text{a sequence }\{a_n\}_{n\ge 1}
\text{ in } A \text{ that converges to } x.
\]
\end{proposition}

\begin{remark}
Recall:
\[
\overline{A}=A\cup A'
\]
\[
x\in A' \Leftrightarrow \exists\ \text{a sequence in } A\setminus\{x\}
\text{ that converges to } x.
\]
\end{remark}

\begin{definition}
Let $(X,d)$ be a metric space and $A\subseteq X$. We say:
\begin{enumerate}[label=\textbf{(\arabic*)}]
  \item a collection of sets $\{U_i\}_{i\in I}$ is an open cover of $A$, if
  $I\neq\varnothing$ is a set, $U_i$ is open $\ \forall i\in I$, and
  \[
  A\subseteq \bigcup_{i\in I} U_i.
  \]
  \item the set $A$ is compact if: $\ \forall\ $ open cover
  $\{U_i\}_{i\in I}$ of $A$, $\exists\ $ a finite set $J\subseteq I$ s.t.
  $\{U_j\}_{j\in J}$ is an open cover of $A$. We call $\{U_j\}_{j\in J}$ a
  finite subcover.
\end{enumerate}
\end{definition}

\begin{example}
Any finite set $\{x_1,\ldots,x_n\}\subseteq X$ is compact.

Let $\{U_i\}_{i\in I}$ be an open cover of $\{x_1,\ldots,x_n\}$.

Then
\[
x_1\in \bigcup_{i\in I} U_i \Rightarrow \exists\, i_1\in I \text{ s.t. } x_1\in U_{i_1}
\]
\[
x_2\in \bigcup_{i\in I} U_i \Rightarrow \exists\, i_2\in I \text{ s.t. } x_2\in U_{i_2}
\]
\[
\vdots
\]

So $\{U_{i_1},\ldots,U_{i_n}\}$ is a finite subcover.
\end{example}

\end{document}
